MINOS Handover Plots

### 2023-07-12 minos/validation/cross_validation.Rmd

---
title: "Cross Validation Analysis"
output: html_notebook
---

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

@@

```{r, include=FALSE}
# cross validation simulation output
#out.path <- 'Minos/output/cross_validation/'
out.path <- here::here('output', 'cross_validation_default/')
cv <- read_singular_local_out(out.path, 'baseline')

# cv simulation pop (not used for transitions)
cv.simul.files <- list.files(here::here('data', 'final_US', 'cross_validation', 'simulation'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw <- do.call(rbind, lapply(cv.simul.files, read.csv))
```

>>>>

---
title: "Cross Validation Analysis"
output:
  html_document:
    df_print: paged
---

@@

workingDir <- here::here()
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

@@

```{r, include=FALSE}
# cross validation simulation output
out.path <- here::here("output", "cross_validation")
cv <- read_singular_local_out(out.path, '/baseline')

# cv simulation pop (not used for transitions)
cv.simul.files <- list.files(here::here('data', 'final_US', 'cross_validation', 'simulation/'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw <- do.call(rbind, lapply(cv.simul.files, read.csv))
```

### 2023-07-12 minos/validation/handovers.Rmd

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

@@

```{r}
start.year <- 2020
save.path <- here::here("plots", "handovers", 'default')
create.if.not.exists(save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'hh_income_wav1.png',
       plot = last_plot(),
       path = save.path)
}

@@

spaghetti_plot(income.spag, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'SF12_wav1.png',
       plot = last_plot(),
       path = save.path)
}

@@

spaghetti_plot(sf12.spag, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

@@

## Financial Situation

```{r}
raw.financial_situation <- raw.dat %>% 
  dplyr::select(pidp, time, financial_situation) %>%
  group_by(time, financial_situation) %>%
  count() %>%
  mutate(source = 'final_US')

base.financial_situation <- base.dat %>%
  dplyr::select(pidp, time, financial_situation) %>%
  group_by(time, financial_situation) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
financial_situation <- rbind(raw.financial_situation, base.financial_situation)
financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)

# Now plot
ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

financial_situation.norm <- financial_situation %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Financial situation') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'financial_situation.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
```

@@

if (shall.we.save) {
  ggsave(filename = 'housing_quality.png',
       plot = last_plot(),
       path = save.path)
}

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, housing_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'housing_quality',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

if (shall.we.save) {
  ggsave(filename = 'neighbourhood_safety.png',
       plot = last_plot(),
       path = save.path)
}

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, neighbourhood_safety)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

if (shall.we.save) {
  ggsave(filename = 'loneliness.png',
       plot = last_plot(),
       path = save.path)
}

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, loneliness)
base.s <- base.dat %>%
  select(pidp, age, time, loneliness)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'loneliness',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

if (shall.we.save) {
  ggsave(filename = 'nutrition_quality_wav1.png',
       plot = last_plot(),
       path = save.path)
}

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, nutrition_quality)
base.s <- base.dat %>%
  select(pidp, age, time, nutrition_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nutrition_quality',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

if (shall.we.save) {
  ggsave(filename = 'physical_health_wav1.png',
       plot = last_plot(),
       path = save.path)
}

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, phealth)
base.s <- base.dat %>%
  select(pidp, age, time, phealth)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'phealth',
             save = shall.we.save,
             save.path = save.path)

rm(raw.s, base.s, spag)
```

## Education

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'Education State'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'education_state.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'education_state')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'education_state',
                 save = shall.we.save,
                 save.path = save.path)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, education_state)
base.s <- base.dat %>%
  select(pidp, age, time, education_state)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'education_state',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

>>>>

require(tidyverse)
require(ggplot2)
require(ggridges) # for densities over time plots. 
require(knitr)
require(here)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
start.year <- 2020

@@

ggsave(filename = 'hh_income_wav1.png',
       plot = last_plot(),
       path = save.path)

@@

spaghetti_plot(income.spag, 'hh_income',
               save = TRUE,
               save.path = save.path)
density_ridges(income.spag, 'hh_income',
               save=TRUE, 
               save.path=save.path)

@@

ggsave(filename = 'SF12_wav1.png',
       plot = last_plot(),
       path = save.path)

@@

spaghetti_plot(sf12.spag, 'SF_12',
               save = TRUE,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

@@

@@

ggsave(filename = 'housing_quality.png',
       plot = last_plot(),
       path = save.path)

@@

@@

ggsave(filename = 'neighbourhood_safety.png',
       plot = last_plot(),
       path = save.path)

@@

@@

ggsave(filename = 'loneliness.png',
       plot = last_plot(),
       path = save.path)

@@

@@

ggsave(filename = 'nutrition_quality_wav1.png',
       plot = last_plot(),
       path = save.path)

@@

@@

ggsave(filename = 'physical_health_wav1.png',
       plot = last_plot(),
       path = save.path)

@@
